% \section{Job Application Letter}

Dear [Name],

Please accept this letter and resume as a part of my application material for the [Position] position. I got to know about this position from the [Offer Source]. After reviewing the qualifications that [Company Name] is seeking, I believe I am a strong candidate with the necessary skills to be successful in this role.

As you will find in my resume, I have had some experience in Software Engineering during my time as a Software Engineer at Technimus Pvt Ltd. Currently pursuing my master's degree at Southern Illinois University Edwardsville, I am eager to apply my technical expertise and problem-solving skills in a real-world setting at [Company Name]. I am particularly excited about the opportunity to contribute meaningfully to [Company Name] through an internship, where I can further develop my abilities while making a positive impact.

During my tenure at Technimus as a Software Engineer, I was involved in developing OSOM: Overseas Student Operation Management. Notably, we built both the UI and API of this application from scratch, step by step, while also conducting client meetings to ensure the goals were aligned. Eventually, when we released the beta version of this application, we closely monitored it and fixed all bugs and issues within minutes of their occurrence. Now in production, the application handles over 500,000 requests monthly, serving more than 15 Education Consultancies across Nepal. This experience taught me the entire process of application production from client requirement analysis, managing feature requests to application monitoring. By utilizing agile methodologies, we were able to iterate quickly based on user feedback, ensuring that our solutions effectively met real-world needs. My experience in taking an application from conception to production, combined with my strong academic background, positions me well to make meaningful contributions to your team.

I would welcome the opportunity to discuss my qualifications for this position in more detail. I appreciate your consideration. I hope to be given the opportunity to contribute to the growth and success of your organization. Please contact me by email at sahrohit9586@gmail.com or phone (+1 618-217-9577) if you have any question about my application materials or wish to arrange a meeting. I look forward to hearing from you soon.