%-------------------------
% Resume in Latex, automated build with github actions
% Author : Rohit Sah
% Github Automation & Builds: https://github.com/sahrohit/sahrohit
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin{document}

% ----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
	\textbf{\Huge \scshape Rohit Kumar Sah} \\ \vspace{1pt}
	\small \href{https://sahrohit.com.np}{\underline{sahrohit.com.np}} $|$ +1 618-217-9577 $|$ \href{mailto:sahrohit9586@gmail.com}{\underline{sahrohit9586@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/sahrohit/}{\underline{linkedin.com/in/sahrohit}} $|$ 
	\href{https://github.com/sahrohit}{\underline{github.com/sahrohit}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Southern Illinois University, Edwardsville, IL}{}
{Master of Science in Computer Science}{(expected 2026)}
\resumeSubheading
{Università degli Studi di Milano Statale, Milan, Italy}{Marks: \textbf{27/30} }
{Foreign Student Exchange Program (Tuiton Fee Waived)}{Feb. 2023 | Jul. 2023}
\resumeSubheading
{Amrita School of Engineering, Chennai, India}{CGPA: \textbf{8.66/10}}
{Bachelor of Technology Computer Science and Engineering (Full-Ride Scholarship)}{Aug. 2019 | Jul. 2023}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Technimus}{Apr. 2024 -- Dec. 2024}
{Software Engineer}{Kathmandu, Nepal}
\resumeItemListStart
\resumeItem{Developed and maintained \textbf{multi-tenant React and Node} applications, \textbf{scaling the platform} to serve over 1M monthly requests while ensuring accessibility and compliance with REST and W3C standards.}
\resumeItem{\textbf{Optimized database schema and queries} in \textbf{multi-schema PostgreSQL databases}, enhancing scalability and reducing query times by 20\%, ensuring high availability and data isolation.}
\resumeItem{\textbf{Attended regular meetings} with team members and clients to track progress, resolve issues, and ensure feature delivery in alignment with client goals, contributing to a 10\% improvement in delivery timelines.}
\resumeItemListEnd

\resumeSubheading
{Tech Central Pvt. Ltd.}{Oct. 2023 -- Apr. 2024}
{Frontend Engineer}{Kathmandu, Nepal}
\resumeItemListStart
\resumeItem{Ensured \textbf{web performance} and \textbf{accessibility} by incorporating Lighthouse metrics into development practices, consistently achieving high scores across all projects.}
\resumeItem{Utilized \textbf{CSS preprocessors (SASS)} with \textbf{BEM patterns} to efficiently style the web application using mobile first style, resulting in a consistent and visually appealing user interface.}
\resumeItem{Streamlined front-end workflows using Gulp to \textbf{automate repetitive tasks} such as minification and compilation; saved an average of 5 hours weekly on manual processes, allowing focus on feature development.}
\resumeItemListEnd

% -----------Multiple Positions Heading-----------
   % \resumeSubSubheading
   %  {Software Engineer I}{Oct 2014 - Sep 2016}
   %  \resumeItemListStart
   %     \resumeItem{Apache Beam}
   %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
   %  \resumeItemListEnd
   % \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://osom.global}{OSOM: Overseas Student Operation Management}} $|$ \emph{React, Typescript, Express} }{Jul. 2024}
\resumeItemListStart
\resumeItem{Developed comprehensive \textbf{CRM} for education consultancies, featuring student management, task tracking, and visa scheduling, serving \textbf{50+ consultancies} in Nepal, processing \textbf{900,000+ monthly network requests.}}
\resumeItem{Integrated student portal featuring document management, visa tracking, and course enrollment systems, while implementing an intuitive, \textbf{feedback-driven} dashboard for \textbf{real-time progress monitoring}.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\href{https://github.com/sahrohit/hex2023}{HEx 2023 Website (Event, Hackathon \& CTF)}} $|$ \emph{Astro, Docker, AWS}}{Jul. 2023}
\resumeItemListStart
\resumeItem{ Volunteered in \textbf{designing} and \textbf{developing} websites for HEx Himalaya, including hackathon, events list, and CTF sites (also member of the CTF organization team) organized by Himalaya College of Engineering.}
\resumeItem{Optimized website to score \textbf{100\% in Lighthouse in all factors} and implemented strategic keywords for top-notch search engine rankings handling over \textbf{25,000 requests in 36 hrs.} timespan.}
\resumeItemListEnd
% \resumeProjectHeading
% {\textbf{\href{https://pracharya.vercel.app}{Pracharya: Mock Test \& Notes Platform}} $|$ \emph{React, Serverless, Typescript}}{Apr. 2024}
% \resumeProjectHeading
% {\textbf{Multi-tenant Ecommerce Platform} $|$ \emph{React, GraphQL, Typescript}}{Jan. 2023 -- Jun. 2023}

% \resumeItemListStart
% \resumeItem{ Highly scalable \textbf{secured} GraphQL API backend with \textbf{fault tolerance} and \textbf{load balancing} with \textbf{TypeORM with Postgres and Redis} to manage user sessions, caching, rate limiting and safe queries to the database.}
% \resumeItem{Developed a storefront using Nextjs and ChakraUI to build \textbf{user-friendly} and \textbf{human centric} design.}
% \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\setlength\itemsep{-2pt}
	\small{\item{
		\textbf{Web Developement}{: React.js, TypeScript, Graphql, Node.js, Express.js, Next.js, Zustand, TRPC, Tailwind CSS} \\
		}
		\item{
		      \textbf{Database \& Streams}{: PostgreSQL, Firebase, Redis, MySQL, Drizzle, Kysely} \\
		}
		\item{
		      \textbf{Data Science}{: Sci-kit Learn, Weka, NumPy, Pandas, PyTorch,  Observable, D3.js} \\
		}
		\item{
		      \textbf{Productivity Boost}{: Git, VS Code, Vim (Basics), Bash, AWS, Docker, Microsoft Office Suite}
	}
 }
\end{itemize}



%----------- OTHERS -----------
\section{Other Details}
\begin{itemize}[leftmargin=0.15in, label={}]
	\setlength\itemsep{-2pt}
	\small{
\item{
		      \textbf{Scholarships:}{ Compex Scholarship Program (Indian Embassy, Nepal) | Mahatma Gandhi Scholarship.} \\
		}

\item{
		      \textbf{Research Paper:}{ Sah R., Amrutha G., Manasa, Chapagain B., \& Padmavathi A. Performance Evaluation of Movie-Based Recommendation Systems using Hybrid Machine Learning Models. International Conference on IoT Based Control Networks and Intelligent Systems ICICNIS 2023.
		      	} \\
		}
		
		\item{
		      \textbf{Relevant Courses:}{ Linear Algebra, Probability \& Stats, Big Data Analytics, Machine Learning, etc.} \\
		}

    	
 
 \item{
		\textbf{Additional Activity:}{ Mentor for Cognizance (College Club) for 2 years | Live-in-Labs (Research for development \& sustainable solutions) | Mentor and Core Organization Team for Hex Himalaya Website, Hackathon, CTF, etc.} | Volunteered in Traffic Policing |  Bungee jumped from the world's 2nd highest platform. \\
		}

		\item{
		      \textbf{Languages:}{ English (fluent) | Nepali (fluent) | Hindi (conversational) | Japanese (beginner)}
	}
 
 	% \item{
		%       \textbf{Tests:}{ IELTS | 7.0 (Listening - 8.0, Reading - 7.0, Writing - 6.0, Speaking - 6.5) , GRE | 316 (Verbal - 154, Quantitative - 162, Analytical Writing - 3.5)} \\
		% }
 }
\end{itemize}

%-------------------------------------------
\end{document}
